full title

### 2020-11-03 paper/pldi21/intro.tex
Minor change in intro
Revised motivation

In this paper, we propose a novel \textit{dynamic shortcut} technique to
leverage high performance of dynamic analysis for static analysis by freely
switching between them in a sound way.  Our key observation is that we can
use concrete semantics for specific program parts while preserving the soundness
if they are not dependent with meaning of abstract values.  For example, the
third line of the following program passes the abstract value \jscode{absval}
stored in \jscode{obj.p1} to the variable \jscode{x}:
\begin{lstlisting}[style=myJSstyle,numbers=none]
var absval = ... // an abstract value
var obj = { p1: absval }, y = "p";
x = obj[y + 1];
\end{lstlisting}
Even though \jscode{obj} contains an abstract value \jscode{absval}, the
semantics of the third line does not dependent with the meaning of
\jscode{absval}.  To utilize this observation in dynamic shortcut, we introduce
\textit{sealed symbolic execution}, which is an augmented concrete execution
with sealed symbolic values.  We represent each abstract value as a sealed
symbolic value, which is a symbolic value that throws an error when trying to
access its actual meaning.  To evaluate our approach, we implemented $\tool$ by
extending the existing JavaScript static analyzer SAFE with dynamic shortcut.
For evaluation of $\tool$, we analyzed abstracted versions of \inred{77}
official tests of \inred{Lodash 4} library.

>>>>

In this paper, we propose a novel \textit{dynamic shortcut} technique to
leverage high performance of dynamic analysis for static analysis by freely
switching between them in a sound way.  Our key observation is that we can
use concrete semantics for specific program parts while preserving the soundness
if they are not dependent with meaning of abstract values.  For example, the
third line of the following program passes the abstract value \jscode{v} stored
in \jscode{obj.p1} to the variable \jscode{x}:
\begin{lstlisting}[style=myJSstyle,numbers=none]
var v = ... // an abstract value
var obj = { p1: v }, y = "p";
x = obj[y + 1];
\end{lstlisting}
Even though \jscode{obj} contains an abstract value \jscode{v}, the semantics of
the third line does not dependent with the meaning of \jscode{v}.  To utilize
this observation in dynamic shortcut, we introduce \textit{sealed symbolic
execution}, which is an augmented concrete execution with sealed symbolic
values.  We represent each abstract value as a sealed symbolic value, which is a
symbolic value that detects when trying to access its actual meaning.  To
evaluate our approach, we implemented $\tool$ by extending the existing
JavaScript static analyzer SAFE with dynamic shortcut.  For evaluation of
$\tool$, we analyzed abstracted versions of \inred{77} official tests of
\inred{Lodash 4} library.

### 2020-11-03 paper/pldi21/motivation.tex
Revised motivation

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle]
function concat() {
  var length = arguments.length;
  if (!length) return [];
  var args = Array(length - 1),
      array = arguments[0],
      index = length;
  while (index--)
    args[index-1] = arguments[index];
  return arrayPush(
    isArray(array) ? copyArray(array) : [array],
    baseFlatten(args, 1));
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Lodash's \jscode{concat} function.}
    \label{fig:concat}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
function changeCountry(G) {
  ...
  if (G.selectedVal === "US" && state) {
    // deterministic arguments of `concat`
    state.items = _.concat([["Other", "Other"]],
      WebinarBase.questions.state.items);
    state.selectedVal = _.head(_.head(C.items));
  }
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load the list of states of the United States.}
    \label{fig:changeCountry}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
function getData(e) {
  var option = ... // option of server connection
  post(option).then(function(e) {
    if (e.total_records && e.total_records > 0) {
      // non-deterministic arguments of `concat`
      this.pastEvents =
        _.concat(this.pastEvents, e.events);
      this.total = e.total_records;
    } else this.noPastData = !0
  })
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load more Zoom events from the server.}
    \label{fig:getData}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
  in \code{zoom.us} site.}
  \label{fig:example}
\end{figure}

In this section, we first point out limitations that existing techniques face to
analyze the real-world example described in Figure~\ref{fig:example}.
We then show how our combined analysis increase the analysis scalability and
precision through lazy concrete execution, seamlessly combined with the original
static analysis.

We excerpt the \jscode{concat} function in Figure~\ref{fig:concat} from Lodash
library~\cite{lodash} (v4.17.20), which is the most popular npm package~\footnote{https://www.npmjs.com/browse/depended}
that \inred{124,562} npm packages depend on.
The \jscode{concat} function creates a new array concatenating given arrays or
values.
It first checks the length of arguments in line 2-3. Then, it stores the first
argument to \jscode{array} in line 5 and copies the remaining arguments to
\jscode{args} in line 7-8.
Finally, it creates a new array by copying the given array via \jscode{copyArray}
or initializing with a single value in line 10, and pushes each element of
\jscode{args} after flattening it via \jscode{baseFlatten} in line 11.

A low degree of context sensitivity tends to face spurious callee explosion
during analyzing \jscode{concat} function.
The analysis is not supposed to lose precision for the loop in line 7-8.
Moreover, \jscode{baseFlatten} has a recursive call in a loop that is a
traditional challenge for static analysis.

We excerpt two functions \jscode{changeCountry} in Figure~\ref{fig:changeCountry}
and \jscode{getData} in Figure~\ref{fig:getData} from the \code{zoom.us}~\cite{zoom}
site.
The website \code{zoom.us} is ranked at \inred{16th} popular web site accroding
to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

When the given arguments of a function invokation are concrete values, we can
perform dynamic analysis instead of static analysis. For example, The
\jscode{changeCountry} function is invoked when a country different with the
current one is selected in registration of Zoom meetings.  When the ``United
States of America'' (USA) is selected, it calls the \jscode{concat} function
with two pre-defined concrete values as arguments to load USA state information
in line 17-18.  The first argument is an array literal \jscode{[["Other",
"Other"]]} and the second one is an array of pairs of abbreviations and names of
USA states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
\jscode{concat} funciton with \jscode{\_} as \jscode{this} value and above two
concrete values as arguments.  It increases performance of static analysis by
skipping the analysis of function call in line 17-18 and utilizing the result of
dynamic analysis.

Dynamic analysis is still applicable using lazy concrete execution even if the
arguments are not concrete values.  The \jscode{getData} function is another
part to use \jscode{concat} function but we can only partially apply dynamic
analysis in this case.  It is invoked when loading more Zoom events in
``Webinars \& Events'' page.  At the first time, initial eight events are stored
in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
\jscode{getData} sends a POST request to the server and receives additional
event information \jscode{e} in line 24.  Then, eight events in
\jscode{e.events} are appended to \jscode{this.pastEvents} using the
\jscode{concat} function in line 27-28.  In this case, arguments are not
deterministic but dependent on the given data from the server.  However, we know
that the number of arguments are still deterministically defined as \jscode{2}
and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
because it just checks the length of \jscode{arguments} and passes its elements
to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
able to be evaluated using concrete semantics because we know that \code{array}
is an abstract array.  Only copying via \jscode{copyArray}, flattening via
\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
semantics.  This is the core idea of lazy concrete execution to maximize the
part of dynamic analysis during static analysis.

In the remaining section we formally define the combined analysis with lazy
concrete execution in Section~\ref{sec:formal}.  Then, we explain how to define
the combined analysis for JavaScript programs in Section~\ref{sec:javascript}.

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle]
function concat() {
  var length = arguments.length;
  if (!length) return [];
  var array = arguments[0],
      args  = Array(length - 1),
      index = length;
  while (index--)
    args[index-1] = arguments[index];
  return arrayPush(isArray(array) ?
    copyArray(array) : [array],
    baseFlatten(args, 1));
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Lodash's \jscode{concat} function.}
    \label{fig:concat}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=13]
function changeCountry(G) {
  ...
  if (G.selectedVal === "US" && state) {
    // deterministic arguments of `concat`
    state.items = _.concat([["Other", "Other"]],
      WebinarBase.questions.state.items);
    state.selectedVal = _.head(_.head(C.items));
  }
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load the list of states of the United States.}
    \label{fig:changeCountry}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \begin{lstlisting}[style=myJSstyle,firstnumber=22]
function getData(e) {
  var option = ... // option of server connection
  post(option).then(function(e) {
    if (e.total_records && e.total_records > 0) {
      // non-deterministic arguments of `concat`
      this.pastEvents =
        _.concat(this.pastEvents, e.events);
      this.total = e.total_records;
    } else this.noPastData = !0
  })
}
    \end{lstlisting}
    \vspace*{-1em}
    \caption{Load more Zoom events from the server.}
    \label{fig:getData}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Motivating Example: Excerpts from Lodash library and JavaScript codes
  in \code{zoom.us} site.}
  \label{fig:example}
  \vspace*{-1em}
\end{figure}

In this section, we will explain the motivation of the dynamic shortcut for
JavaScript static analysis with real-world examples described in
Figure~\ref{fig:example}.  We first describe their program behaviors and then
explain how to utilize dynamic analysis during static analysis of them.

For motivating examples, we excerpt the \jscode{concat} function in
Figure~\ref{fig:concat} from Lodash library~\cite{lodash} (v4.17.20), which is
the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
and \inred{124,562} npm packages have dependency with it.  The \jscode{concat}
function creates a new array concatenating given arrays or values.  It first
checks the length of arguments in line 1-3. Then, it stores the first argument
to \jscode{array} in line 4 and copies the remaining arguments to \jscode{args} in
line 5-8.  In line 9, it checks whether \jscode{array} is an array object with
the built-in function \jscode{isArray}.  If so, it creates a new array by
copying the given array via or initializing with a single value in line 10.
Finally, it flattens \jscode{args} via \jscode{baseFlatten} and pushes the
result to the new array in line 11.

For applications of Lodash, we excerpt two functions \jscode{changeCountry} in
Figure~\ref{fig:changeCountry} and \jscode{getData} in Figure~\ref{fig:getData}
from the \code{zoom.us}~\cite{zoom} site.  The website \code{zoom.us} is
homepage of Zoom, which is a videotelephony software program developed by Zooom
Video Communications and it is ranked as \inred{16th} popular web site according
to Alexa\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

\paragraph{Dynamic shortcut with concrete values.}
When the given arguments of a function are concrete values, we can perform
dynamic analysis instead of static analysis. For example, the
\jscode{changeCountry} function is invoked when a user selects another country
on the drop-down list in the registration page.  It calls the \jscode{concat}
function to update the drop-down list of states or provinces in 17-18.  However,
when the user selects ``United States of America'' (USA), two arguments are
pre-defined with deterministic values; the first one is an array literal
\jscode{[["Other", "Other"]]} and the second one is an array of pairs of
abbreviations and names of the states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
\jscode{concat} function with \jscode{\_} as \jscode{this} value and above two
concrete values as arguments.  It increases performance of static analysis by
skipping the analysis of function call in line 17-18 and utilizing the result of
dynamic analysis.

\begin{figure}[t]
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \top & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \symb_\jscode{int}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{this.pastEvents}}
    \label{fig:pastEvents}
  \end{subfigure}
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \jscode{0} & \symb_\jscode{evt}\\\hline
        \cdots & \cdots\\\hline
        \jscode{7} & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \jscode{8}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{e.events}}
    \label{fig:events}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Concrete objects for arguments with sealed symbolic values.}
  \label{fig:sealed}
  \vspace*{-1em}
\end{figure}

\paragraph{Dynamic shortcut with abstract values.}
Dynamic analysis is still applicable using \textit{sealed symbolic execution}
even if the arguments are not concrete values.  The \jscode{getData} function is
invoked when clicking the ``Load More'' button to load more Zoom events in
``Webinars \& Events'' page.  For each click, the \jscode{getData} sends a POST
request to the server and receives additional event information \jscode{e} in
line 24.  Then, eight events in \jscode{e.events} are appended to
\jscode{this.pastEvents} using the \jscode{concat} function in line 27-28.
However, the arguments of \jscode{concat} are not deterministic because 1) the
event list stored in \jscode{this.pastEvents} is continuously grown for each
load and 2) also each event stored in \jscode{e.events} are dependent on the
data given from the server.

To perform dynamic analysis with abstract values, we sealed the abstract values
of arguments with symbolic values as described in Figure~\ref{fig:sealed}.  It
contains two symbolic values $\symbevt$ and $\symbint$ that represent any event
objects and integer values, respectively.  Then, dynamic analysis is
successfully performed before copying \jscode{array} via \jscode{copyArray} in
line 10.  First, \jscode{length} stores \jscode{2} and passes the length check
in line 1-2. Then, \jscode{array} points to the same object of
\jscode{this.pastEvents} in line 4, \jscode{args} stores an array with a
single object stored in \jscode{e.events} in 5-8, and the \jscode{isArray}
function returns \jscode{true} for \jscode{array} in line 9.  However, it fails
to perform dynamic analysis for \jscode{copyArray} because the \jscode{length}
property of \jscode{array} is the symbolic value $\symbint$.  Thus, the dynamic
shortcut returns the analysis result and the static analyzer continues to
analyze the program from line 10.  Then, only copying via \jscode{copyArray},
flattening via \jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize
the abstract semantics.  This is how to utilize sealed symbolic execution to
maximize the part of dynamic analysis during static analysis.

\paragraph{Dynamic shortcut for opaque functions.}

The previous two examples also show that dynamic shortcut can improve the
analysis precision and lessen the effort of modeling the opaque functions.
In line 9, the \jscode{isArray} function is a JavaScript built-in library thus
it is written in a native language of the host environment.  Thus, we need to
manually model its behavior to statically analyze it.  Assume that we model the
\jscode{isArray} function to return the top boolean value that denotes both of
\jscode{true} and \jscode{false}.  If we perform static analysis with this
modeling, both of true branch \jscode{copyArray(array)} and false branch
\jscode{[array]} in line 10 are always analyzed while \jscode{[array]} is never
reachable in the motivating examples.  However, with the dynamic shortcut, the
analyzer utilizes the concrete semantics of \jscode{isArray}.  It returns more
precise result \jscode{true} instead of the top boolean value and it is not
necessary to model the \jscode{isArray} function for static analysis of
motivating examples.
